---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
unzip("activity.zip")
dd <- read.csv("activity.csv", stringsAsFactors=FALSE)
dd$date <- as.Date(dd$date, format="%Y-%m-%d")
str(dd)

```

NEED TO MERGE HOURS MINS DATE!!!


## What is mean total number of steps taken per day?
Prepare dataset of daily steps
```{r}
agg <- aggregate(steps ~ date, data=dd, sum)
```

Histogram of daily steps
```{r}
hist(agg$steps, main="Steps per day", xlab="Steps")
```
Mean
```{r}
mean(agg$steps)
```
Median
```{r}
median(agg$steps)
```




## What is the average daily activity pattern?
Create dataset of average steps per 5 minute time chunk
```{r}
agg <- aggregate(steps ~ interval, data=dd, mean, na.rm=TRUE)
agg$interval2 <- agg$interval/100
```
```{r}
plot(steps ~ interval2, agg, type="l", xaxt="n", xlab="Time")
axis(1, at=seq(0, .24, .06), labels=c("00:00", "06:00", "12:00", "18:00", "24:00"))
```




## Imputing missing values
Vector of mean values matching the appropriate values in original data...
```{r}
steps <- agg$steps[match(dd$interval, agg$interval)]
```
Replace by the mean value
```{r}
dd2 <- dd
dd_imp$steps[is.na(dd_imp$steps)] <- steps[is.na(dd_imp$steps)]
```







## Are there differences in activity patterns between weekdays and weekends?
