---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}

# setwd("DataScienceCoursera/RepData_PeerAssessment1/")
# unzip("activity.zip")
dd <- read.table("activity.csv", stringsAsFactors=FALSE, sep=",", head= TRUE)
dd$date <- as.Date(dd$date, format="%Y-%m-%d")
str(dd)

```

## What is mean total number of steps taken per day?
Prepare dataset of daily steps
```{r}
agg <- aggregate(steps ~ date, data=dd, sum)
```

Histogram of daily steps
```{r}
hist(agg$steps, main="Steps per day", xlab="Steps")
```

Mean
```{r}
mean(agg$steps)
```

Median
```{r}
median(agg$steps)
```




## What is the average daily activity pattern?
Create dataset of average steps per 5 minute time chunk
```{r}
agg <- aggregate(steps ~ interval, data=dd, mean, na.rm=TRUE)
```

Use chron:::time to define a time series and avoid straight stretches representing the nonexistant 45 mins between HH55 and HH00.

```{r}
library(chron)
agg$t <- time(agg$interval)
```

```{r}
plot(steps ~ t, agg, type="l", xaxt="n", xlab="Time")
axis(1, at=seq(0, nrow(agg), 72), labels=c("00:00", "06:00", "12:00", "18:00", "24:00"))
```

Most steps at 
```{r}
agg$interval[agg$steps == max(agg$steps)]
```
which presumably corresponds to the travel to work or pre-work sports.

## Imputing missing values
Vector of mean values matching the appropriate values in original data...
```{r}
steps <- agg$steps[match(dd$interval, agg$interval)]
```

Replace missing values by the mean value at that time point
```{r}
dd2 <- dd
dd2$steps[is.na(dd2$steps)] <- steps[is.na(dd2$steps)]
```

Histogram of mean steps per day
```{r}
agg <- aggregate(steps ~ date, data=dd2, sum)
```

Histogram of daily steps
```{r}
hist(agg$steps, main="Steps per day", xlab="Steps")
```






## Are there differences in activity patterns between weekdays and weekends?

```{r}
dow <- day.of.week(month = as.numeric(format(dd2$date, format = "%m")), day = as.numeric(format(dd2$date, format = "%d")), year = as.numeric(format(dd2$date, format = "%Y")))

dd2$weekend <- dow %in% c(0,6)
dd2$weekend[dd2$weekend] <- "Weekend"
dd2$weekend[dd2$weekend=="FALSE"] <- "Weekday"

agg <- aggregate(steps ~ interval + weekend, dd2, mean)

for(i in c("Weekend", "Weekday")){
  agg$t[agg$weekend == i] <- time(agg$interval[agg$weekend == i])
}

library(lattice)

xyplot(steps ~ t | weekend, data= agg, layout=c(1, 2), scales=list(at=seq(0, nrow(agg), 72), x.labels=c("00:00", "06:00", "12:00", "18:00", "24:00")), xlab="Time", type="l")

```

As one might expect, the user was generally up earlier during the weekdays and was generally less active throughout the day than at weekends.









